The evolution of the transcriptome of mammalian placentas

### 2016-09-08 manuscript/common_latex.tex
we're only showing the top 40 genes in the type III anova
update the gene tree explanation

\newcommand{\genetreeexplanation}[2][1]{Gene tree and heatmap of
  expression of genes related to #2. The gene tree was obtained from
  Ensembl~\cite{Cunningham.ea2015:Ensembl2015} and genes from species
  not included in this study or having expression by FPKM less than #1
  were excluded from the plotted tree. Heatmap cells in white are from
  species where there was no expression of the relevant transcript (or
  a species where that transcript does not apply). The species names
  are abbreviated with the first letter of the genus and first two
  letters of the species (for example, \textit{Homo sapiens} is
  \textit{H.sa.}). Genes with duplicate gene names in the same species
  (or no gene named defined) are listed by the Ensemble gene ID.}

@@

\newcommand{\lineagetableexplanationtypeiii}[2]{%
  \lineagetableexplanation[A nested type-III anova was used to
  calculate p values.]{#1}{#2}}

>>>>

\newcommand{\genetreeexplanation}[2][1]{Gene tree showing expression
  and ancestral expression of genes related to #2. The gene tree was
  obtained from Ensembl~\cite{Cunningham.ea2015:Ensembl2015} and genes
  from species not included in this study were excluded from the
  plotted tree. The coloring of the internal nodes of the plots
  indicates the ancestral expression as estimated by fastAnc using
  phylotools. Genes with duplicate gene names in the same species (or
  no gene named defined) are listed by the Ensemble gene ID with
  leading zeros elided.}

@@

\newcommand{\lineagetableexplanationtypeiii}[2]{%
  \lineagetableexplanation[A nested type-III anova was used to
  calculate p values, and the top 40 genes by $\text{log}_2$
  Fold-Change which changed significantly (FDR $\le 0.05$) are
  shown. ]{#1}{#2}}
